\chapter{Conclusion}
	
	In this thesis project, we created heterogeneous 1D and 2D simple cell and tissue models and simulated unbiased diffusion of non-interacting particles in these systems using lattice Monte Carlo (MC) and lattice master equation (ME) methods. 
	
	There were two main goals in this project. The first goal was to develop two computational methods that could be used as alternatives to simulate diffusion in systems that might otherwise be very difficult to simulate by solving the diffusion equation (with the appropriate boundary conditions). The MC method used, sometimes known as a particle-based method, can provide particle trajectory information, but is relatively slow and computed density distributions suffer from statistical fluctuations. The ME method used was a distribution-based approach; the particle density was evolved in time. Its evolution represented the average behaviour of infinitely many particles and therefore it can be said that with an increasing number of particles used, the MC method approaches the ME method. The ME method is unable to provide particle trajectory information but ME simulations are much faster to compute. For our purposes, data for analysis was provided by ME simulations. The second goal was to perform analyses of diffusion in simple 1D and 2D heterogeneous systems built from unit cells. More specifically, we analyzed how changing different parameters such as the: semi-permeable boundary transition probabilities, region diffusivities, and cell geometry (2D only), affected the diffusion behaviour and long-time effective diffusivity. When a specific parameter was tested, all other parameters were held constant.
	
	\newpage
	
	All heterogeneous systems were characterized by equal-sized, cellular and extracellular regions of different diffusivities repeating in series and separated by semi-permeable boundaries. The 2D systems included an extracellular channel in which there were no obstacles and particles could pass through freely. The systems as a whole were enclosed by reflecting absolute boundaries. Since diffusion was unbiased, it was expected that the long-time particle density distribution is equal everywhere. In order for that to occur, it was necessary to use a semi-permeable boundary condition called the ``iso-thermal" condition, which can be derived using detailed balance theory. This boundary condition specifically relates/couples the boundary transition probabilities between regions of different diffusivities.
	
	For all heterogeneous systems studied, normal and sub- and/or super-diffusive behaviour was observed. Normal diffusive behaviour was characterized by a computed mean-squared-displacement (MSD) that scaled linearly in time ($ \textrm{MSD} \propto t $). For sub-diffusive behaviour, $ \textrm{MSD} \propto t^{\beta < 1} $, and for super-diffusive behaviour, $ \textrm{MSD} \propto t^{\beta > 1} $. In general, the semi-permeable boundary acts to impede or slow particle diffusion, therefore causing temporary sub-diffusive behaviour as particles begin to interact with a boundary. If the region outside the starting region of the particles is of higher diffusivity, super-diffusive behaviour follows after sub-diffusive behaviour. In the long-time limit, diffusive behaviour returns to normal.
	
	For 1D heterogeneous systems, we have shown that sub- and super-diffusive behaviours occur. However, for the cell geometry and sizes used, the magnitude of super-diffuse behaviour was very small or non-existent. With decreasing boundary transition probability, the magnitude of sub-diffusive behaviour increased. For all transition probabilities tested and with increasing probability, the long-time effective diffusivity was less than but approached the diffusivity of the starting region. Additionally, with varying transition probability, there was a large variance in the long-time effective diffusivity. For all cellular-extracellular diffusivity ratios (C/EC) tested, only sub-diffusive behaviour was observed and the long-time effective diffusivities were less than the starting region diffusivities. For varying diffusivity ratios, the variance in the long-time effective diffusivity was large.
	
	For 2D heterogeneous systems, the presence of the extracellular channel made a significant impact on both the diffusive behaviour and long-time effective diffusivity. Super-diffusive behaviour was much more prominent; it was comparable in magnitude to the sub-diffusive behaviour. In contrast to the results from the 1D simulations, for all transition probabilities tested, the long-time effective diffusivity was greater than the starting region diffusivity. Additionally, the variance in the long-time effective diffusivity was relatively small. Again, in contrast to the results from the 1D simulations, for all C/EC diffusivity ratios tested, sub- and super-diffusive behaviour was observed. Interestingly, the long-time effective diffusivity calculated was practically independent of the C/EC diffusivity ratio. Given the importance of the extracellular channel, varying channel widths were also tested. In a system with no extracellular channel (pseudo-1D system), only sub-diffusive behaviour occurred. An extracellular channel width of even a single (1) lattice site results in super-diffusive behaviour. Further increasing the width of the extracellular channel increases the magnitude of the super-diffusive behaviour and long-time effective diffusivity. Increasing the width of the channel makes more of the highly diffusive extracellular space available for the particles, therefore it is expected that larger channel widths result in greater long-time effective diffusivities, but only up to the limit of the extracellular diffusivity.
	
	Overall, the extracellular channel acts as a conduit where particles may travel unobstructed. The presence of the extracellular channel results in super-diffusive behaviour of a greater magnitude, increased long-time effective diffusivities, and the possibility that the ratio of cellular to extracellular diffusivities does not have a major impact on the long-time effective diffusivity.
	
	\newpage
	
	In the end, some `future work' remains. First, a correction factor must be determined and applied to the relation used to calculate the effective diffusivity in the 2D systems. The MSD calculation used to determine the effective diffusivity only used the x-position of particles since the systems studied were much larger in $ \hat{x} $ than in $ \hat{y} $. This means that for some time steps, the calculated MSD was no different than the previous calculation since no movement occurred in $ \hat{x} $, but movement did occur in $ \hat{y} $. Second, simulation time and length needs to be mapped to physical time and length. Lastly, parameter space for the simulations needs to be explored further; the diffusive behaviours are well understood but the calculated effective diffusivity in the long-time and its exact dependence on different parameters mostly remains a mystery.