	\begin{algorithm}[h]
		%\KwData{this text}
		\label{alg:1D-MC}
		\caption{1D Monte Carlo}
		(\textsl{initialization of all necessary variables and array structures})\;
		\For(\tcc*[h]{for every time-step...}){$ t = 1, 2, 3, \cdots, t_{\textrm{max}} $}{
			\For(\tcc*[h]{loop over every particle...}){$ n = 1, 2, 3, \cdots, N$}{
				determine which unit cell the particle is in\;
				determine where in the unit cell the particle is located\;	  	
				\eIf{particle is in cellular region}{
					assign particle state: cellular\;
				}
				{
					assign particle state: extracellular\;
				}
				\BlankLine
				\tcc{Determine possible particle movement using a test position. The particle's position does not change.}
				\eIf{particle state: cellular}{
					\tcc{Cellular directional stepping probabilities used.}
					draw pseudo-random number ($ rnd $) from uniform distribution\;
					\uIf{$ \textrm{rnd} < P_{x,i} $}{
						generate particle test position if to move one unit $ -x $\;
					}
					\uElseIf{$  \textrm{rnd} < P_{x,i} + P_{x,i} $}{
						generate particle test position if to move one unit $ +x $\;
					}
					\Else{
						generate particle test position if to stay in current position\;
					}
				}
				{
					\tcc{Extracellular stepping probabilities used.}
					draw pseudo-random number ($ rnd $) from uniform distribution\;
					\uIf{$ \textrm{rnd} < P_{x,e} $}{
						generate particle test position if to move one unit $ -x $\;
					}
					\uElseIf{$  \textrm{rnd} < P_{x,e} + P_{x,e} $}{
						generate particle test position if to move one unit $ +x $\;
					}
					\Else{
						generate particle test position if to stay in current position\;
					}	
				}
				\pagebreak
				\BlankLine
				\tcc{Particle movement depends on the test position.}
				determine which unit cell the test position is in\;
				determine where in the unit cell test position is located\;
				\eIf{particle test position is in cellular region}{
					assign particle test state: cellular\;			
				}
				{
					assign particle test state: extracellular\;
				}
				\BlankLine
				\uIf{state == teststate}{
					\tcc{Particle has not moved to different region.}
					set new particle position to test position\;
				}
				\uElseIf{state == cellular \& teststate == extracellular}{
					\tcc{Particle is in cellular region at boundary.}
					draw pseudo-random number ($ rnd $) from uniform distribution\;
					tbd\;
				}
				\Else{
					tbd\;
				}
			}
		}
		\KwResult{Particle density distribution at every time step.}
			 
	\end{algorithm}